---
title: "Pure baskets chi-square"
author: "Maria Zarifyan"
date: "27 December 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#https://github.com/cran/RVAideMemoire/blob/master/R/chisq.multcomp.R

chisq.multcomp <-
function(x,p.method="fdr") {
  x <- sort(x)
  fun.p <- function(i,j) {
    xi <- x[i]
    xj <- x[j]
    suppressWarnings(chisq.test(c(xi, xj)))$p.value
  }
  tab.p <- pairwise.table(fun.p,as.character(x),p.adjust.method=p.method)
  call <- match.call()
  dname.x <- if(length(call$x)==1) {call$x} else {paste(call$x[1],"(",paste(call$x[-1],collapse=","),")",sep="")}
  result <- list(method="chi-squared tests",data.name=dname.x,p.adjust.method=p.method,p.value=tab.p)
  class(result) <- "pairwise.htest"
  return(result)
}
```


## close-close meton
LIT = literal, 
CM1 = close meton 1
CM2 = close meton 2
```{r}
baskets = c(CM1=656, CM2=739, LIT=1142)
sum(baskets)/3
```

```{r}
chisq.test(baskets)
```
```{r}
chisq.multcomp(baskets)
```
All three types of baskets are significantly different from each other 

## close-far meton
LIT = literal, 
CM = close meton 
FM = far meton 
```{r}
baskets = c(CM=724, FM=957, LIT=852)
chisq.test(baskets)
```

```{r}
chisq.multcomp(baskets)
```
All three types of baskets are significantly different from each other 

## close meton
LIT = literal, 
METON = meton
METAPH = metaph
```{r}
baskets = c(LIT=921, METON=666, METAPH=1623)
sum(baskets)
```
```{r}
chisq.test(baskets)
```
```{r}
chisq.multcomp(baskets)
```
All three types of baskets are significantly different from each other 

## far meton
LIT = literal, 
METON = meton
METAPH = metaph
```{r}
baskets = c(LIT=1227, METON=892, METAPH=1599)
sum(baskets)
```
```{r}
chisq.test(baskets)
```

```{r}
chisq.multcomp(baskets)
```
All three types of baskets are significantly different from each other 
